\documentclass[11pt]{article}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}

\usepackage{float}
\usepackage{enumitem}
\usepackage{commath}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{cancel}
\usepackage{subfigure}
\usepackage{multicol}

\usepackage{graphicx}
\graphicspath{{images/}}

\usepackage{my_notes}
\usepackage{my_math}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}

\newenvironment{just}{\textit{Justification.}}{}
\newenvironment{trans}{\textit{Translation.}}{}

\setlength\parindent{0pt}

\newcommand{\pder}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\der}[2]{\frac{d{#1}}{d{#2}}}

\begin{document}

\title{Differential Equations}
\author{Sean Richardson}
\date{\today}
\maketitle

\section{}
\begin{definition}
There are three general approaches to solving differential equations.
    \begin{itemize}
        \item An \emph{analytic} approach is to use a method that provides
            a formula for the exact solution.
        \item A \emph{qualitative} approach is to look at different
            properties or sketch to get a feel for the solution.
        \item A \emph{numeric} approach is approximate the solution with
            guess/check.
    \end{itemize}
\end{definition}

Some basics of differential equations:
\begin{itemize}
    \item A differential equation relates some function to some derivative
        of itself.
    \item We solve for \emph{functions}.
    \item Functions of one variable are ``ordinary differential
        equations'' (ODE's). Functions of multiple variables are called
        ``partial differential equations'' (PDE's).
\end{itemize}

\section{Models}
\subsection{Exponential Model}
/**/
\begin{equation}
    \der{P}{t} = kP
\end{equation}
/*solution*/
/*slope field*/

\subsection{Logistic Model}
/*graph motivation*/
\begin{align}
    \frac{1}{P}\der{P}{t}=-\frac{k}{M}P+k \nonumber \\
    \der{P}{t}=Pk(1-\frac{P}{M})
\end{align}
/*solution*/
/*slope field*/

\section{}
\begin{theorem}[Fundamental Theorem of ODE's]
    Suppose $f(t,y)$ is a function which $x$ is continuous and has
    continuous $\pder{f}{y}$ in some neighborhood $(t_0,y_0)$. Then, the
    IVP $$
    \begin{cases}
        y(t_0) = y_0 \\
        \der{y}{t} = f(t,y)
    \end{cases} $$
    has a unique solution.
\end{theorem}

\end{document}


