\documentclass[11pt]{article}

\usepackage{amsmath}
\usepackage{amsthm}

\usepackage{my_notes}
\usepackage{my_math}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}

\newenvironment{just}{\textit{Justification.}}{}
\newenvironment{trans}{\textit{Translation.}}{}

\title{Theory of Computation}
\author{Sean Richardson}
\date{\today}

\begin{document}

\maketitle

\section{}

\begin{definition}[Alphabet]
An \emph{alphabet} is a non-empty set. The members of an alphabet are
\emph{symbols}.
\end{definition}

\begin{definition}[String]
    A \emph{string} is a sequence of symbols from the alphabet. $\epsilon$
    is the empty string. For a string $w$ The length of the string sequence
    is denoted $\myabs{w}$
\end{definition}

\begin{definition}[Finite Automaton]
    Formally, a \emph{finite automaton} is a 5-tuple
    $(Q,\Sigma,\delta,q_0,F)$, where
    \begin{itemize}
        \item $Q$ is the finite set called the \emph{states}.
        \item $\Sigma$ is a finite set called alphabet.
        \item $\delta: Q \times \Sigma \rightarrow Q$ is the transition
            function.
        \item $q_0 \in Q$ is the start state.
        \item $F \subseteq$ is a set of accept states.
    \end{itemize}
\end{definition}

/*State diagram*/

\begin{definition}
    Let $M= (Q,\Sigma,\delta,q_0,F)$. If $M$ takes the string
    $w=w_1w_2\dots w_n$, then $M$ \emph{accepts} $w$ if a sequence of states
    ${r_0,r_1,\dots r_n}$ exists such that:
    \begin{itemize}
        \item $r_0 = q_0$
        \item $\delta (r_i,w_{i+1})=r_{i+1}$ for $0 \leq i \leq n-1$
        \item $r_n \in F$
    \end{itemize}
\end{definition}

\begin{definition}
    For a finite automaton $M$, we say \emph{$M$ recognizes language $A$}
    if $A = \{ w \mid M \text{ accepts } w \}$.
\end{definition}

\begin{definition}[Regular Language]
    A language is called a \emph{regular language} if some finite automaton
    recognizes it.
\end{definition}

\end{document}
